Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion

### 2018-09-26 outputs/docs/events/svm-rmarkdown-article-example.tex
Update paper and add voting data

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 24
September 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent Government policy is partly driven by the topics that are discussed in
parliament. Conversely, those same topics can indicate a government's
priorities. But major events--both expected, such as an election, and
unexpected, such as a recession or terrorist attack--can affect the
course of parliamentary debate. In this paper, we systematically analyse
how parliamentary debate has changed in response to different types of
events in Australian history. We compile a dataset of what was said in
Australian state and federal parliaments from the mid-1800s through to
2017 based on available public records. We use a structural text model
to reduce the dimensionality of the text and to impose prior knowledge
such as correlation between days and changes over time. We then examine
the effect of various events using a discrete choice model. We find
that: 1) changes of government are associated with topic changes only
when there is also a change of the party in power; and 2) economic
events, such as financial crises, have significant and persistent
effects. Our findings have implications for how we think about the
longer-term trajectory of government policy as the media cycle becomes
increasingly focused on short-term events.

@@

Australian Hansard records have been analysed for various purposes,
usually at smaller-scale. For instance, \citet{Rasiah2010} examined
Hansard records for the Australian House of Representatives to examine
whether politicians attempted to evade questions about Iraq during
February and March 2003. And \citet{GansLeigh2012} examined Australian
Hansard records to associate mentions by politicians of certain public
intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
There is a more limited set of XML records available in some
cases.\footnote{Tim Sherratt makes these XML records available as a
  single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through today from Open Australia's website.} There are
65,000 \textbf{{[}UPDATE{]}} Hansard records publicly available across
the state and federal parliaments (Table 1) \textbf{{[}UPDATE
NUMBERING{]}}. As with any larger-scale data process, there are various
issues with some of the PDFs and the known ones are detailed in the
Appendix.

@@

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in the Appendix. The full set of
  scripts are available on request.} These scripts are primarily based
on: the \texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified. The \texttt{hunspell} package of
\citet{Ooms2017} is also used to help find spelling issues.

\textbf{{[}ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT
RECORD?{]}}

@@

Text usually needs to be pre-processed before topic models can be used.
The specific steps that we take are to remove numbers and punctuation
and to change all the words to lower case. Then the sentences are
deconstructed and each word considered individually. In addition to the
packages already mentioned, in this step the R scripts to do this use
the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.

@@

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments. However these had many
errors and were supplemented by data from the Australian Dictionary of
Biography and Wikipedia.\footnote{An example of the additional
  information is provided in the Appendix. The datasets are available on
  request.}

@@

The main models that we use in this paper are the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}, and a discrete choice model as
implemented by the \texttt{XXXX} R package of \textbf{XYZ}. In theory we
could have directly used the text as an input to the discrete choice
model, but this is intractable due to computer memory and storage
constraints. Instead, in a similar way to \citet{MuellerRauh2018}, we
use the topics that the text is about as an input to another model,
which in our case is a discrete choice model.

@@

Although more- or less-fine levels of analysis are possible, but here we
are primarily interested in considering a day's topics. This means that
each day's Hansard record needs to be classified by its topics.
Sometimes Hansard records includes titles that make the topic clear. But
not every statement has a title and the titles do not always define
topics in a well-defined and consistent way, especially over longer time
periods. One way to get consistent estimates of the topics discussed in
Hansard is to use the LDA method of \citet{Blei2003latent}, for instance
as implemented by the R package `topicmodels' by \citet{Grun2011}.

The key assumption behind the LDA method is that each day's text, `a
document', in Hansard is made by speakers who decide the topics they
would like to talk about in that document, and then choose words,
`terms', that are appropriate to those topics. A topic could be thought
of as a collection of terms, and a document as a collection of topics,
where these collections are defined by probability distributions. The
topics are not specified \emph{ex ante}; they are an outcome of the
method. In this sense, this approach can be considered unsupervised
statistical learning. Terms are not necessarily unique to a particular
topic, and a document could be about more than one topic. This provides
more flexibility than other approaches such as a strict word count
method. The goal is to have the words found in each day's Hansard group
themselves to define topics.

@@

The distinguishing aspect of the Structural Topic Model (STM) of
\citet{RobertsStewartAiroldi2016} is that it includes additional
information about documents. For instance, in general we usually have
some information about the author and date of a document. In the case of
Hansard, we know who was speaking and the date. STM allows this
additional information to affect the construction of topics, though
influencing either topical prevalence or topical content. That said, the
assumption that there is some document generation process is the same as
the LDA method, it is just that this process now includes metadata.

The STM is set-up to most easily include metadata to do with prevalence
and content. Prevalence relates to the topic proportions in each
document. For instance, we expect that topics related to the reasons for
Federation such as tariffs and trade should be more prevalent in those
earlier years than later. Similarly, we may expect topics to do with
terrorism to be more prevalent in recent years than in earlier ones.
Content relates to the words that make up each topic. For instance,
there are changes in the use of language over the period for which we
have data, and it would be better for these to not be responsible for
defining different topics rather than being part of the same topic.

The document generation process of \citet{Blei2003latent} discussed
earlier is modified slightly by \citet{RobertsStewartAiroldi2016}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The proportion of a document dedicated to a topic is drawn ``from a
  logistic-normal generalised linear model based on a vector of document
  covariates \(X_d\)'':
  \[\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \sigma)\]
  ``where \(X_d\) is a 1-by-p vector, \(\gamma\) is a p-by-K - 1 matrix
  of coefficients and \(\sigma\) is K-1 by K-1 covariance matrix.''
  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.}
\item
  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.} Given a document-level
  content covariate \(y_d\), form the document-specific distribution
  over words representing each topic (\(k\)) using the baseline word
  distribution \(m\), the topic specific deviation, \(\kappa_k^{(t)}\),
  the covariate group deviation, \(\kappa_{y_d}^{(c)}\), and the
  interaction between the two, \(\kappa_{y_{d}k}^{(i)}\):
  \[\beta_{d,k}\sim exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) \]
\end{enumerate}

HERE

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  There are For each topic, decide the terms that the topic uses by
  randomly drawing distributions over the terms. The distribution over
  the terms for the \(k\)th topic is \(\beta_k\). Typically a topic
  would be a small number of terms and so the Dirichlet distribution
  with hyperparameter \(0<\eta<1\) is used:
  \(\beta_k \sim \mbox{Dirichlet}(\eta)\).\footnote{The Dirichlet
    distribution is a variation of the beta distribution that is
    commonly used as a prior for categorical and multinomial variables.
    If there are just two categories, then the Dirichlet and the beta
    distributions are the same. In the special case of a symmetric
    Dirichlet distribution, \(\eta=1\), it is equivalent to a uniform
    distribution. If \(\eta<1\), then the distribution is sparse and
    concentrated on a smaller number of the values, and this number
    decreases as \(\eta\) decreases. A hyperparameter is a parameter of
    a prior distribution.} Strictly, \(\eta\) is actually a vector of
  hyperparameters, one for each \(K\), but in practice they all tend to
  be the same value.
\end{enumerate}

STM can be implented using the stm R package of
\citet{RobertsStewartAiroldiRPackage}.

@@

We consider the effect of political, economic, and other events on
Australian parliamentary discussion. Political events are those related
to a change of government or an election (Tables \ref{tab:governments}
and \ref{tab:elections}). Economic events are defined by substantial
changes in various economic measures, such as the onset of the Great
Depression or the Great Recession (Table \ref{tab:economicevents}).
Other events are those such as the 9/11 attacks, or the Bali Bombing
(Table \ref{tab:otherevents}). The list of events that we consider is
detailed in .

@@

\subsection{External events}\label{external-events}

@@

@@

>>>>

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 25
September 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent Government policy is partly driven by parliamentary discussion.
Conversely, that same discussion can indicate a government's priorities.
But major events--both expected, such as an election, and unexpected,
such as a recession or terrorist attack--can affect the course of
parliamentary discussion. In this paper, we systematically analyse how
parliamentary discussion changes in response to different types of
events in Australian history. We compile a dataset of what was said in
Australian state and federal parliaments from the mid-1800s through to
2017 based on available public records. We use a structural text model
to reduce the dimensionality of the text and to impose prior knowledge
such as correlation between days and changes over time. We then examine
the effect of various events using a discrete choice model. We find
that: 1) changes of government are associated with topic changes only
when there is also a change of the party in power; and 2) economic
events, such as financial crises, have significant and persistent
effects. Our findings have implications for how we think about the
longer-term trajectory of government policy as the media cycle becomes
increasingly focused on short-term events.

@@

Australian Hansard records have been analysed for various purposes. For
instance, \citet{Rasiah2010} examined Hansard records for the Australian
House of Representatives to examine whether politicians attempted to
evade questions about Iraq during February and March 2003. And
\citet{GansLeigh2012} examined Australian Hansard records to associate
mentions by politicians of certain public intellectuals with neutral or
positive sentiment.

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
An example of what a page of Hansard looks like is included in Appendix
\textbf{{[}ADD NUMBERING{]}}. There is a more limited set of XML records
available in some cases.\footnote{Tim Sherratt makes these XML records
  available as a single download and also presents them in a website
  (historichansard.net/) that can be used to explore Commonwealth
  Hansard records from 1901 to 1980. Commonwealth XML records from 1998
  to 2014 are available from Andrew Turpin's website, and from 2006
  through to today from Open Australia's website. The records can also
  be downloaded from the Australian Hansard website.} There are 65,000
\textbf{{[}UPDATE{]}} Hansard records publicly available across the
state and federal parliaments (Table 1) \textbf{{[}UPDATE NUMBERING{]}}.
As with any larger-scale data process, there are various issues with
some of the PDFs and the known ones are detailed in Appendix
\textbf{{[}ADD NUMBERING{]}}.

@@

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in Appendix \textbf{{[}ADD
  NUMBERING{]}}. The full set of scripts are available on request.}
These scripts are primarily based on: the \texttt{PDFtools} package of
\citet{Ooms2018pdftools}; the \texttt{tidyverse} package of
\citet{Wickham2017}; the \texttt{tm} package of
\citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified. The \texttt{hunspell} package of
\citet{Ooms2017} is also used to help find spelling issues.

@@

Text usually needs to be pre-processed before topic models can be used.
The specific steps that we take are to remove numbers and punctuation
and to change all the words to lower case. Then the sentences are
deconstructed and each word considered individually. In addition to the
packages already mentioned, in this step the R scripts to do this use
the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
\textbf{NEED TO bundle\_ngrams i.e.~olive oil should be olive\_oil, not
considered separately.}

@@

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments. However these had many
errors and were supplemented by data from the Australian Dictionary of
Biography and Wikipedia.\footnote{An example of the additional
  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The
  datasets are available on request.}

@@

The main models that we use in this paper are the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}, and a discrete choice model as
implemented by the \texttt{XXXX} R package of \textbf{XYZ}. In theory we
could have directly used the text as an input to the discrete choice
model, but this quickly becomes intractable due to computer memory and
storage constraints. Instead, in a similar way to
\citet{MuellerRauh2018}, we use the topics that the text is about as an
input to another model, which in our case is a discrete choice model. In
Appendix \textbf{{[}ADD NUMBERING{]}}, we include an alternative
approach that follows \citet{Taddy2015} by using word2vec, which more
closely uses words, rather than topics, as an input.

@@

Although more- or less-fine levels of analysis are possible, but here we
are primarily interested in considering a day's topics. This means that
each day's Hansard record needs to be classified by its topics.
Sometimes Hansard records includes titles that make the topic clear. But
not every statement has a title and the titles do not always define
topics in a well-defined and consistent way, especially over longer time
periods. One way to get consistent estimates of the topics discussed in
Hansard is to use the LDA method of \citet{Blei2003latent}, for instance
as implemented by the R \texttt{topicmodels} package of
\citet{Grun2011}.

The key assumption behind the LDA method is that each day's text, `a
document', in Hansard is made by speakers who decide the topics they
would like to talk about in that document, and then choose words,
`terms', that are appropriate to those topics. A topic could be thought
of as a collection of terms, and a document as a collection of topics,
where these collections are defined by probability distributions. The
topics are not specified \emph{ex ante}; they are an outcome of the
method. In this sense, this approach can be considered unsupervised
machine learning. Terms are not necessarily unique to a particular
topic, and a document could be about more than one topic. This provides
more flexibility than other approaches such as a strict word count
method. The goal is to have the words found in each day's Hansard group
themselves to define topics.

@@

The distinguishing aspect of the Structural Topic Model (STM) of
\citet{RobertsStewartAiroldi2016} is that it considers more than just a
document's content when constructing topics. For instance, we generally
have some information about the author and the date that a document was
created. In the case of Hansard, we know who was speaking and the date
they spoke. STM allows this additional information to affect the
construction of topics, though influencing either topical prevalence or
topical content. That said, the assumption that there is some document
generation process is the same as the LDA method, it is just that this
process now includes metadata.

The STM is set-up to most easily include metadata to do with prevalence
and content. Prevalence relates to the topic proportions in each
document. For instance, we expect that topics related to the reasons for
Federation, such as tariffs and trade, should be more prevalent in those
earlier years than later. Similarly, we may expect topics to do with
terrorism to be more prevalent in recent years. Content relates to the
words that make up each topic. For instance, there are changes in the
use of language over the period for which we have data, and it would be
better for these to not be responsible for defining different topics
rather than being part of the same topic.

Again, the assumed process that generates the documents is the key
aspect as this will be reversed to estimate the topics. The document
generation process of \citet{Blei2003latent} discussed earlier, is
slightly modified by \citet{RobertsStewartAiroldi2016} for the STM:

\textbf{THIS NEEDS WORK START}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The proportion of a document dedicated to a topic, stored in the
  vector \(\theta_d\), is drawn from a logistic-normal distribution,
  parameterised such that the mean of that distribution, \(\mu\), is
  affected by a document covariates, \(X_d\), following
  \citet{RobertsStewartTingley2018}:
  \[\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)\]
  ``where \(X_d\) is a 1-by-p vector, \(\gamma\) is a p-by-K - 1 matrix
  of coefficients and \(\sigma\) is K-1 by K-1 covariance matrix.'' This
  is in contrast to the Dirichlet distribution that characterises LDA.
\item
  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.} Given a document-level
  content covariate \(y_d\), form the document-specific distribution
  over words representing each topic (\(k\)) using the baseline word
  distribution \(m\), the topic specific deviation, \(\kappa_k^{(t)}\),
  the covariate group deviation, \(\kappa_{y_d}^{(c)}\), and the
  interaction between the two, \(\kappa_{y_{d}k}^{(i)}\):
  \[\beta_{d,k}\propto exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) \]
\end{enumerate}

\textbf{THIS NEEDS WORK END}

We implement the STM on the daily-level parliamentary text data
described earlier using the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. We consider both topic prevalence
and content to be functions of time. The choice of how many topics to
use in the model is a situation-specific compromise. We use standard
diagnostic techniques to decide on 80 topics, and more detail on this
process is available in Appendix \textbf{{[}ADD NUMBERING{]}}.

One way to summarise the results of the topic model is to \textbf{????}

@@

We consider the effect of political, economic, and other events on
Australian parliamentary discussion. Political events are those related
to a change of government or an election. Economic events are defined by
substantial changes in various economic measures, such as the onset of
the Great Depression or the Great Recession. Other events are those such
as the 9/11 attacks, or the Bali Bombing. The full list of events that
we consider is detailed in Appendix \textbf{{[}ADD NUMBERING{]}}. We
consider events in two ways. The first is in the change in the word
usage before and after events and the second is in changes in the
topics.

Differences in word usage can be evaluated using the term
frequency-inverse document frequency (tf-idf) measure. It will be higher
for words that are rarely used across all documents, but commonly used
in a document. For instance, in Australian parliamentary text records
`the' is commonly used in many documents and so the fact that it is used
in any particular document is not usual. However, `aboriginal' is less
common across, and so if it was especially prevelant in a particular
document that may distinguish that document.

When we consider events using tf-idf, we gather terms from more than one
day. We define groups of days that are roughly analogous to sitting
periods. If there is more than a week between a day then we define a new
group, otherwise the day is in the existing group. We use various
measures \textbf{(Text2vec R package has some? or some other package)}
to define a baseline measure of how different each group is, and then
test for whether groups separated by our events are significantly
different to this baseline.

Changes in topics also help define how \ldots{}

@@

\subsection{Other events}\label{other-events}

@@

\subsection{Example page}\label{example-page}

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/example_hansard_page} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\subsection{Events}\label{events}

\subsection{Choosing number of topics}\label{choosing-number-of-topics}

Add the graphs and procedures.

\subsection{word2vec alternative}\label{word2vec-alternative}

An alternative approach that follows \citet{Taddy2015}.
